---
title: "Formal Demography at IUSSP 2021"
output: 
  html_document:
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
render_toc <- function(
  filename, 
  toc_header_name = "Table of Contents",
  base_level = NULL,
  toc_depth = 1
) {
  x <- readLines(filename, warn = FALSE)
  x <- paste(x, collapse = "\n")
  x <- paste0("\n", x, "\n")
  for (i in 5:3) {
    regex_code_fence <- paste0("\n[`]{", i, "}.+?[`]{", i, "}\n")
    x <- gsub(regex_code_fence, "", x)
  }
  x <- strsplit(x, "\n")[[1]]
  x <- x[grepl("^#+", x)]
  if (!is.null(toc_header_name)) 
    x <- x[!grepl(paste0("^#+ ", toc_header_name), x)]
  if (is.null(base_level))
    base_level <- min(sapply(gsub("(#+).+", "\\1", x), nchar))
  start_at_base_level <- FALSE
  x <- sapply(x, function(h) {
    level <- nchar(gsub("(#+).+", "\\1", h)) - base_level
    if (level < 0) {
      stop("Cannot have negative header levels. Problematic header \"", h, '" ',
           "was considered level ", level, ". Please adjust `base_level`.")
    }
    if (level > toc_depth - 1) return("")
    if (!start_at_base_level && level == 0) start_at_base_level <<- TRUE
    if (!start_at_base_level) return("")
    if (grepl("\\{#.+\\}(\\s+)?$", h)) {
      # has special header slug
      header_text <- gsub("#+ (.+)\\s+?\\{.+$", "\\1", h)
      header_slug <- gsub(".+\\{\\s?#([-_.a-zA-Z]+).+", "\\1", h)
    } else {
      header_text <- gsub("#+\\s+?", "", h)
      header_text <- gsub("\\s+?\\{.+\\}\\s*$", "", header_text) # strip { .tabset ... }
      header_text <- gsub("^[^[:alpha:]]*\\s*", "", header_text) # remove up to first alpha char
      header_slug <- paste(strsplit(header_text, " ")[[1]], collapse="-")
      header_slug <- tolower(header_slug)
    }
    paste0(strrep(" ", level * 4), "- [", header_text, "](#", header_slug, ")")
  })
  x <- x[x != ""]
  knitr::asis_output(paste(x, collapse = "\n"))
}
```



Here is a list of formal demography presentations at the [IUSSP International Population Conference](https://ipc2021.popconf.org/), to be held 5-10 December. Papers are organized chronologically within broad themes. 

If you or someone you know is presenting formal demography work and it is not included on the list below, please fill out [this form](https://docs.google.com/forms/d/e/1FAIpQLSfKxR-KnFvhwyfEqFdC24DeucArPrMCb0MAKT_2oV_TO1QFMg/viewform). 

**Note: Submissions received after 4 December may not be added to this webpage in time for your presentation!!**

Check out presentations in the following categories:

```{r}
render_toc("iussp.Rmd")
```


### Economic Demography

#### Monday, December 6

- '[Female Labour Force Participation in Sub-Saharan Africa: A Cohort Analysis](https://ipc2021.popconf.org/abstracts/210810)', Andreas Backhaus & Elke Loichinger. [Session 28](https://ipc2021.popconf.org/sessions/28) (14:00-15:30 UTC). 
- '[Unequal Duties and Unequal Retirement: Decomposing the Women’s Labor Force Decline in Post-reform China](https://ipc2021.popconf.org/abstracts/210422)', Kai Feng. [Session 28](https://ipc2021.popconf.org/sessions/28) (14:00-15:30 UTC). 
- '[The Motherhood Penalty in the Brazilian Labor Market: An Age-Period-Cohort Analysis](https://ipc2021.popconf.org/abstracts/211717)', Iracy Pimenta, Simone Wajnman, & Gilvan R. Guedes. [Session 28](https://ipc2021.popconf.org/sessions/28) (14:00-15:30 UTC). 

#### Tuesday, December 7

- '[Global Population Change & Economic Convergence of World Countries: Meaning and Implications for Global Inequality](https://ipc2021.popconf.org/abstracts/211738)', Parfait Eloundou-Enyegue, Sarah Giroux, Mila Cantar, Shoshanna Hoover, Kristie Lebeau, Kimberly Pollock, Clara Rice, & Michael Zhang. [Session 88](https://ipc2021.popconf.org/sessions/88) (22:00-23:30). 

#### Thursday, December 8

- '[Population Aging and Retirement Age Policy: Period Balances, Generational Imbalances](https://ipc2021.popconf.org/abstracts/211460)', Fernando Fernandes, Cassio M. Turra, & Eduardo L. G. Rios-Neto. [Session 172](https://ipc2021.popconf.org/sessions/172) (18:00-19:30 UTC).
- '[Savings and the Demographic Dividend: Evidence from a Macrosimulation Model](https://ipc2021.popconf.org/abstracts/211612)', Joshua K. Wilde & Mahesh Karra. [Session 143](https://ipc2021.popconf.org/sessions/143) (08:00-09:30 UTC). 

#### Friday, December 9

- '[Labour Force Projections in India until 2060 and Implications for the Demographic Dividend](https://ipc2021.popconf.org/abstracts/210098)', Guillaume Marois, Ekaterina Zhelenkova, & Balhasan Ali. [Session 189](https://ipc2021.popconf.org/sessions/189) (12:00-13:30 UTC). 
- '[Poverty, Education and Human Capital in India: The Age Education Structure](https://ipc2021.popconf.org/abstracts/211593)', Sayeed Unisa, Tejal Lakhan, & Neethu Naik. [Session 189](https://ipc2021.popconf.org/sessions/189) (12:00-13:30 UTC). 



### Fertility, Family Planning, and Reproductive Health 

#### Monday, December 6


- '[Female Genital Mutilation/Cutting in the Central African Republic: A Demographic Perspective](https://ipc2021.popconf.org/abstracts/210532)', José Antonio Ortega. [Session 8](https://ipc2021.popconf.org/sessions/8) (08:00-09:30 UTC). 
-  '[Improving Methodology for Fertility Forecasting through the Incorporation of Individual-Level Data and Population-Level Parity Information](https://ipc2021.popconf.org/abstracts/210191)', Joanne Ellison, Ann M. Berrington, Erengul Dodd, Jonathan J. Forster, & Jakub Bijak. [Session 39](https://ipc2021.popconf.org/sessions/39) (18:00-19:30 UTC).
- '[China’s Low Fertility May Not Hinder Future Prosperity](https://ipc2021.popconf.org/abstracts/210431)', Guillaume Marois, Stuart Gietel-Basten, & Wolfgang Lutz. [Session 9](https://ipc2021.popconf.org/sessions/9) (08:00-09:30 UTC). 
-  '[Imputation of Full Birth Histories from Census Data: A Rediscovered Method for the Detailed Analysis of Fertility](https://ipc2021.popconf.org/abstracts/211656)', Ian Timeaus. [Session 39](https://ipc2021.popconf.org/sessions/39) (18:00-19:30 UTC).

#### Tuesday, December 7

- '[Bayesian Projections of the Total Fertility Rate for Improvements in Education and Family Planning](https://ipc2021.popconf.org/abstracts/210521)', Daphne Liu & Adrian Raftery. [Session 88](https://ipc2021.popconf.org/sessions/88) (22:00-23:30). 

- '[Is NRR Time-Sensitive in Measuring Population Replacement Level?](https://ipc2021.popconf.org/abstracts/210503)', Arni Rao. [Session 83](https://ipc2021.popconf.org/sessions/83) (18:00-19:30 UTC).

- '[Future Levels of Fertility in Sub-Saharan Africa: Parity-Based Projections](https://ipc2021.popconf.org/abstracts/210891)', Thomas Spoorenberg & Mathias Lerch. [Session 88](https://ipc2021.popconf.org/sessions/88) (22:00-23:30). 


#### Wednesday, December 8

- '[Age Patterns of Contraceptive Use and Needs: A Global Comparison](https://ipc2021.popconf.org/abstracts/211737)', Vladimira Kantorova, Mark Wheldon, Philipp Ueffing, & Aisha Dasgupta. [Session 117](https://ipc2021.popconf.org/sessions/117) (14:00-15:30 UTC). 
- '[Global Changes in Contraceptive Method MIX and Outlook to 2030](https://ipc2021.popconf.org/abstracts/210339)', Philipp Ueffing, Vladimira Kantorova, Mark Wheldon, Joseph Molitoris, & Aisha Dasgupta. [Session 117](https://ipc2021.popconf.org/sessions/117) (14:00-15:30 UTC). 

- '[Country-Level Patterns in Unintended Pregnancy and Abortion 2015–2019: A Description of Country-Specific Estimates from a Bayesian Hierarchical Model](https://ipc2021.popconf.org/abstracts/210329)', Jonathan Bearak, Anna Popinchalk, Cynthia Beavin, Bela Ganatra, Ann-Beth Moller, Özge Tunçalp, & Leontine Alkema. [Session 128](https://ipc2021.popconf.org/sessions/128) (18:00-19:30 UTC). 


#### Thursday, December 9

- '[Probabilistic Projection of Subnational Total Fertility Rate in India and Its 15 Major States, 1950-2100](https://ipc2021.popconf.org/abstracts/211221)', Ankita Srivastava & Nandita Saikia. [Session 138](https://ipc2021.popconf.org/sessions/138) (04:00-05:30 UTC). 

- '[Fertility in Italian Regions: Analysis and Estimation of Cohort Indicators](https://ipc2021.popconf.org/abstracts/210849)', Sara Miccoli. [Session 144](https://ipc2021.popconf.org/sessions/144) (08:00-09:30 UTC).

- '[Approaches to Study Parity Progression of Fertility with illustrative application to India’s National Family Health Survey](https://ipc2021.popconf.org/abstracts/211337)', Padum Narayan & Arvind Pandey. [Session 147](https://ipc2021.popconf.org/sessions/147) (10:00-11:30 UTC).

#### Friday, December 10

- '[Fertility Transition in Ethiopia: A Study Using Reproductive Outcome Measures of Bongaarts and Casterline](https://ipc2021.popconf.org/abstracts/210314)', Mezgebo Gebretsadikan & Krishna Ponnapalli. [Session 179](https://ipc2021.popconf.org/sessions/179) (06:00-07:30 UTC)
- '[Low Fertility in Tehran: An Agent-Based Modeling Approach](https://ipc2021.popconf.org/abstracts/211657)', Mohammad Jalal Abbasi-Shavazi, Nasibeh Esmaeili, Hajiieh Bibi Razeghi Nasrabad, & Fatemeh Torabi. [Session 179](https://ipc2021.popconf.org/sessions/179) (06:00-07:30 UTC)
- '[Scenario-Based Fertility Projections Incorporating Impacts of COVID-19](https://ipc2021.popconf.org/abstracts/210288)', Ann M. Berrington, Joanne Ellison, Bernice Kuang, Sindhu Vasireddy,& Hill Kulu. [Session 179](https://ipc2021.popconf.org/sessions/179) (06:00-07:30 UTC)

- '[Estimating Contraceptive Needs in the Postpartum Period: A Population-Level Comparison of Five Measures of Unmet Need and Demand for Contraception among Women in Ethiopia](https://ipc2021.popconf.org/abstracts/211077)', Celia Karp, Sophia Magalona, Solomon Shiferaw, Assefa Seme, & Linnea Zimmerman. [Session 196](https://ipc2021.popconf.org/sessions/196) (14:00-15:30 UTC). 


### Migration

#### Monday, December 6

- '[Modeling and Forecasting Bilateral Migration Flows for All Countries](https://ipc2021.popconf.org/abstracts/210639)', Nathan Welch & Adrian Raftery. [Session 34](https://ipc2021.popconf.org/sessions/34) (16:00-17:30 UTC). 
- '[Estimates of Migration Flows and Recent Immigration Stocks in Latin America. How Much Are They Alike?](https://ipc2021.popconf.org/abstracts/210651)', Julieta Bengochea, Emanuele Del Fava, Victoria Prieto Rosas, & Emilio Zagheni. [Session 34](https://ipc2021.popconf.org/sessions/34) (16:00-17:30 UTC). 
- '[Assessing the Demographic Impact of Migration on the Working Age Population in European Regions](https://ipc2021.popconf.org/abstracts/210392)', Daniela Ghio, Anne Goujon, & Fabrizio Natale. [Session 9](https://ipc2021.popconf.org/sessions/9) (08:00-09:30 UTC). 



#### Tuesday, December 7

- '[Gender and Educational Differences in Internal Migration](https://ipc2021.popconf.org/abstracts/210664)', Guy J. Abel, Aude Bernard, & Raya Muttarak. [Session 45](https://ipc2021.popconf.org/sessions/45) (04:00-05:30 UTC).


- '[Cross National Comparisons of the Drivers of Rural-Urban Migration Based on Millions of Individual Census Records](https://ipc2021.popconf.org/abstracts/210861)', Ziyue Huang. [Session 45](https://ipc2021.popconf.org/sessions/45) (04:00-05:30 UTC). 
- '[Marriage Migration in India: The Enlargement of Marriage Markets in the Era of Declining Sex Ratios](https://ipc2021.popconf.org/abstracts/211126)', Enu Anand. [Session 45](https://ipc2021.popconf.org/sessions/45) (04:00-05:30 UTC). 

- '[How Can Migration, Workforce Participation, and Education Balance the Cost of Aging in Europe?](https://ipc2021.popconf.org/abstracts/210099)', Guillaume Marois, Alain Bélanger, & Wolfgang Lutz. [Session 51](https://ipc2021.popconf.org/sessions/51) (08:00-09:30 UTC). 
- '[Would Sustained Immigration Prevent Long-Run Population Decrease in European Countries?](https://ipc2021.popconf.org/abstracts/210304)', Nick Parr. [Session 51](https://ipc2021.popconf.org/sessions/51) (08:00-09:30 UTC). 
- '[Age- And Sex-Specific Estimates of Migration Flows in Asia-Pacific](https://ipc2021.popconf.org/abstracts/210301)', Tianyu Shen, James Raymer, & Qing Guan. [Session 88](https://ipc2021.popconf.org/sessions/88) (22:00-23:30). 
- '[Integrating Expert Opinions and Data to Estimate and Forecast International Migration](https://ipc2021.popconf.org/abstracts/210416)', Arkadiusz Wisniowski. [Session 88](https://ipc2021.popconf.org/sessions/88) (22:00-23:30).  

#### Wednesday, December 8

- '[Estimating Migration Flows between Europe and Regions of the World](https://ipc2021.popconf.org/abstracts/211824)', Georgios Aristotelous, [Session 111](https://ipc2021.popconf.org/sessions/111) (12:00-13:30 UTC).
- '[Analysing the Uncertainty of Migration Scenarios through Macroeconomic Models](https://ipc2021.popconf.org/abstracts/211826)', Emily Barker, [Session 111](https://ipc2021.popconf.org/sessions/111) (12:00-13:30 UTC).
- '[Internal Migration and Life Course Transitions in Brazil](https://ipc2021.popconf.org/abstracts/210800)', Reinaldo Santos, Alisson F. Barbieri, & Ernesto Amaral. [Session 111](https://ipc2021.popconf.org/sessions/119) (14:00-15:30 UTC).

#### Thursday, December 9

- '[Bayesian Estimation and Projections of Internal Migration Flows in Italy](https://ipc2021.popconf.org/abstracts/211055)', Emanuela Furfaro, Federico Castelletti, & Adrian Raftery. [Session 170](https://ipc2021.popconf.org/sessions/170) (16:00-1730 UTC). 
- '[Novel Approaches Based on Sequences Analysis and Graphs for Grasping Complexity of Migrations](https://ipc2021.popconf.org/abstracts/211243)', Francois Mialhe, Florence De Longueville, Samuel Bonnand, & Sabine J. F. Henry. [Session 170](https://ipc2021.popconf.org/sessions/170) (16:00-1730 UTC). 
- '[The Mobility Transition in Asia between 1970-2011](https://ipc2021.popconf.org/abstracts/210740)', Wanli Nie, Ashira Menashe-Oren, & Philippe Bocquier. [Session 170](https://ipc2021.popconf.org/sessions/170) (16:00-1730 UTC). 
- '[Practical Geospatial and Sociodemographic Predictors of Human Mobility](https://ipc2021.popconf.org/abstracts/210821)', Corrine Ruktanonchai, Shengjie Lai, Chigozie E Utazi, Adam Sadilek, Andrew J. Tatem, & Alessandro Sorichetta. [Session 170](https://ipc2021.popconf.org/sessions/170) (16:00-1730 UTC). 

#### Friday, December 10

- '[Where Are the Spaniards Moving after the Outbreak of the COVID-19 Pandemic?](https://ipc2021.popconf.org/abstracts/210979)', Miguel González-Leonardo & Antonio Lopez-Gay. [Session 180](https://ipc2021.popconf.org/sessions/180) (08:00-09:30 UTC). 


### Mortality and Health

#### Monday, December 6

- '[When Do Parents Bury a Child? Uncertainty of Offspring Loss across the Demographic Transition](https://ipc2021.popconf.org/abstracts/210202)', Diego Alburez-Gutierrez, Ugofilippo Basellini, & Emilio Zagheni. [Session 26](https://ipc2021.popconf.org/sessions/26) (14:00-15:30 UTC).

#### Tuesday, December 7

- '[Estimating and Forecasting Age-Specific Maternal Mortality Rates in Brazil](https://ipc2021.popconf.org/abstracts/211061)', Bernardo L. Queiroz, Marcia C. Castro, & Ricardo Pedroso. [Session 80](https://ipc2021.popconf.org/sessions/80) (16:00-17:30 UTC). 
- '[Entangling the Economic Impact of Disease on Households in India](https://ipc2021.popconf.org/abstracts/211491)', Srikanth Reddy Umenthala. [Poster Session 7](https://ipc2021.popconf.org/sessions/P7#111) (11:00-12:30 UTC).


#### Wednesday, December 8 

- '[Modelling Weekly Mortality Incorporating Annual Trends](https://ipc2021.popconf.org/abstracts/210936)', Joanne Ellison, Jason Hilton, Erengul Dodd, Jonathan J. Forster, Peter W. F. Smith, & Jakub Bijak. [Session 118](https://ipc2021.popconf.org/sessions/118) (14:00-15:30 UTC).

- '[Regional Mortality Inequalities in the Netherlands and the Role of Internal Migration](https://ipc2021.popconf.org/abstracts/211636)', Adrien Remund, Fanny Janssen, & Ernst van der Hoeven. [Session 119](https://ipc2021.popconf.org/sessions/119) (14:00-15:30 UTC). 

#### Thursday, December 9

- '[Cause of Death Reduce Life Table](https://ipc2021.popconf.org/abstracts/210297)', Vladimir Canudas-Romo, Jose Manuel Aburto, & Marius Pascariu. [Session 135](https://ipc2021.popconf.org/sessions/135) (2:00-03:30 UTC).
-  '[The Sensitivity of the Healthy Life Years Indicator: Approaches for Dealing with Age-Specific Prevalence Data](https://ipc2021.popconf.org/abstracts/211687)', Vanessa di Lego & Markus Sauerberg. [Session 135](https://ipc2021.popconf.org/sessions/135) (2:00-03:30 UTC).
- '[Application of Network Analysis to Multiple Causes of Death Data in Japan](https://ipc2021.popconf.org/abstracts/210680)' Futoshi Ishii, Reiko Hayashi, Emiko Shinohara, & Motomi Beppu. [Session 135](https://ipc2021.popconf.org/sessions/135) (2:00-03:30 UTC).
- '[Indirect Estimation of Life Expectancy by Ethnicity in Chile](https://ipc2021.popconf.org/abstracts/211457)', Moisés Sandoval & Marcela Alvear. [Session 135](https://ipc2021.popconf.org/sessions/135) (2:00-03:30 UTC).
- '[Probabilistic Projection of Subnational Life Expectancy](https://ipc2021.popconf.org/abstracts/211034)', Hana Sevcikova & Adrian Raftery. [Session 135](https://ipc2021.popconf.org/sessions/135) (2:00-03:30 UTC).

- '[Trends and Pattern in Excess Female Under-5 Mortality in India](https://ipc2021.popconf.org/abstracts/210700)', Vandana Tamrakar & Nandita Saikia. [Session 146](https://ipc2021.popconf.org/sessions/146) (08:00-09:30 UTC). 

- '[Lifesaving and a New Ticket to Life: A Reappraisal of the Resuscitation Approach](https://ipc2021.popconf.org/abstracts/211693)', Vanessa di Lego. [Session 166](https://ipc2021.popconf.org/sessions/166) (16:00-17:30 UTC).

#### Friday, December 10

- '[Low-Cost Sibling Methods for Measuring Adult Mortality](https://ipc2021.popconf.org/abstracts/210384)', Bruno Masquelier, Ashira Menashe-Oren, Georges Reniers, & Ian M. Timaeus. [Session 183](https://ipc2021.popconf.org/sessions/183) (18:00-09:30 UTC).

- '[Cosmopolitan Cities or the “Great White North”? A Small-Scale Hierarchical Cluster Analysis of 4,689 Canadian Census Subdivisions](https://ipc2021.popconf.org/abstracts/211530)', Leora Courtney-Wolfman. [Session 197](https://ipc2021.popconf.org/sessions/197) (14:00-15:30 UTC).

### Population Projection and Reconstruction

#### Tuesday, December 7

- '[POPP Project for the Optical Character Recognition of Parisian Population Censuses](https://ipc2021.popconf.org/abstracts/210135)', Sandra Brée, Thierry Paquet, François Merveille, Thomas Constum, Nicolas Kempf, & Pierrick Traounez. [Session 80](https://ipc2021.popconf.org/sessions/80) (16:00-17:30 UTC). 

- '[Forecasting Vital Rates from Demographic Summary Measures](https://ipc2021.popconf.org/abstracts/210318)', Carlo Giovanni G. Camarda & Jose Manuel Aburto. [Session 80](https://ipc2021.popconf.org/sessions/80) (16:00-17:30 UTC). 


### Urban Demography 

#### Monday, December 6

- '[The End of Urban Sprawl? A Swiss Assessment from 1966 to 2018](https://ipc2021.popconf.org/abstracts/210772)', Mathias Lerch. [Session 38](https://ipc2021.popconf.org/sessions/38) (18:00-19:30 UTC).
- '[Toward a Global Urbanization Analysis for Subnational Territories by Exploring Remote Sensing-Based Products](https://ipc2021.popconf.org/abstracts/211058)', Hamidreza Zoraghein & Leiwen Jiang. [Session 38](https://ipc2021.popconf.org/sessions/38) (18:00-19:30 UTC).

#### Tuesday, December 7

- '[Measuring the Concentration of Urban Population in the Negative Exponential Model Using the Lorenz Curve, Gini Coefficient, Hoover Dissimilarity Index, and Relative Entropy](https://ipc2021.popconf.org/abstracts/210120)', Joel Cohen. [Session 83](https://ipc2021.popconf.org/sessions/83) (18:00-1930 UTC).

#### Thursday, December 9

- '[Dynamics of Fertility and Family Planning among the Urban Poor in India: Findings from NFHS 2, 3 and 4](https://ipc2021.popconf.org/abstracts/210038)', Siddharth Agarwal & S Kaushik. [Session 158](https://ipc2021.popconf.org/sessions/158) (14:00-15:30 UTC). 





